Four Problems for Sophistication

### 2015-01-08 Facticity/Facticity/paper.tex
abstract

\begin{abstract}
Kolmogorov complexity is a sound measure of the amount information in a binary string, but it does not distinguish between the information that expresses the structural properties of the data, and noise. Kolmogorov's definition of the \emph{structure function} in his lecture Tallinn in 1973 was the first attempt to separate meaningful information from noise, but many alternative definitions of the \emph{sophistication}, or the amount of meaningful information in the data, have subsequently been proposed. This indicates that the idea is considered worth pursuing by multiple distinguished scholars, but at the same time it shows that the issue has never been resolved completely satisfactorily.

>>>>

\begin{abstract}
Kolmogorov complexity is a sound measure of the amount information in a binary string, but it does not distinguish between the information that expresses the structural properties of the data, and noise. Kolmogorov's definition of the \emph{structure function} in his lecture in Tallinn in 1973 was the first attempt to separate meaningful information from noise, but many alternative definitions of the \emph{sophistication}, or the amount of meaningful information in the data, have subsequently been proposed. This indicates that the idea is considered worth pursuing by multiple distinguished scholars, but at the same time it shows that the issue has never been resolved completely satisfactorily.
